---
title: "Lab 2"
author: Muskaan Mahes
output: pdf_document
date: "2023-09-05"
---
# Question 1

Here is a list of ages of 20 patients below , input it and find out the maximum, the minimum and the average age: 
Use max(), min(), mean()
```{r}
Age <- c(54, 20, 67, 46, 72 ,49 ,61, 46, 36, 31, 52, 73, 56, 75, 59, 42, 31, 73, 43, 22)


```


# Question 2

1) Create a vector x storing the sequence  12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22.

2) Add 2 to the vector x. Save the result into a variable called y.

3) Multiply y by 5. Save that into a variable called z.

4) Subtract 6 from z and divide the result by 3. Save what you get to a variable named answer.

5) Print your answer variable.
```{r}

```

# Question 3

1) Print the grade matrix and check the values are correct


2) Print Student A's Chemistry grade from the grade matrix using the square bracket []


3) Print Student A and B's Chemistry grades from the grade matrix using the square bracket []


4) Select Student A and B's Physics and Calculus grades using [] and save it as a new matrix called grade.math
```{r}
grade=matrix(c(4,3.7,3.3,3.3,3.7,3.7,3,2.7),nrow=2,ncol=4,
             dimnames = list(c("Student A","Student B"), 
                             c("Physics","Chemistry","Calculus","History")))
```

# Question 4

You can select the Calculus grades by std.info$Calculus

1) Print the Student A and B's History grades from std.info using the dollar sign $


2) Print Student B's Home State using the square bracket [] (This is similar to the matrix)
```{r}
std.info = data.frame("Physics" = c(4,3.7), "Chemistry" = c(3.3,3.3),
                      "Calculus" = c(3.7,3.7), "History" = c(3,2.7),
                      "HomeState"= c("Texas","Georgia"))
```

# Question 5

Classify these variables as either Qualitative(Categorical) or Quantitative(numerical)
- Age, State, Weight, Class Section, Ethnicity, GPA
