---
title: "Lab 3"
author: "Nastaran Ghorbani"
date: "2024-09-16"
output: html_document
---



# Question 1
a) Load the dataset provided below. 
b) What are the dimensions of the UN dataset.
```{r}
library(carData)
data(UN)


```


# Question 2

Clean the dataset, by removing the "NA", use na.omit().
```{r}

```



# Question 3
a) What are the mean and range of the fertility variable in the cleaned UN dataset by using mean() and range()?

b) What are the summary statistics of the cleaned UN dataset, and specifically for the fertility variable?

c) What are the first quartile (Q1), third quartile (Q3), and interquartile range (IQR) of the fertility variable in the cleaned dataset?

```{r}

```



# Question 4
What does the boxplot of the fertility variable reveal about its distribution and outliers?

```{r}

```


# Question 5

a) Investigate the correlation between ppgdp variable and lifeExpF. Is there a strong positive or negative correlation between these two variables?

b) Create a frequency table of the variable region.

c) Create a contingency table of countries by their region (region) and group (group).

```{r}
library(tidyverse)

```

